Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-16 nips_2018.tex
visual updates to initial figure, tiny edits

\begin{tabular}{r|c|}\cmidrule{2-2}
  Task&
  \begin{tabular}{rcl}
  Nancy FreeHafer&$\longrightarrow$& Dr. Nancy\\
 Andrew Cencici&$\longrightarrow$&Dr. Andrew\\
 Pushmeet Kohli&$\longrightarrow$&???
  \end{tabular}\\\cmidrule{2-2}
  Program&$f(\text{\code{s}})\,=\,$\code{(}$f_0$\code{ "Dr." (}$f_2$\code{ s " "))}\\\cmidrule{2-2}
  DSL&\begin{tabular}{l}
    $f_0($\code{a}$,$\code{b}$) \,=\, $\code{(fold a b (lambda (x y) (cons x y)))}\\
    \hspace{0.5cm}($f_0$: \emph{Appends lists (of characters))}\\
    $f_1($\code{s}$,$\code{c}$) \,=\, $\code{(fold s s (lambda (x a)}\\
    \phantom{$f_1($\code{s}$,$\code{c}$) \,=\, $\code{  }}\code{(if (= c x) nil (cons x a))))}\\
        \hspace{0.5cm}($f_1$: \emph{Take characters from }\code{s}\emph{ until }\code{c}\emph{ reached)}
    \end{tabular}\\\cmidrule{2-2}
  \end{tabular}

@@

Because any model may be encoded as a (deterministic or probabilistic) program,
we carefully delineate the scope of program learning problems considered here.
We think of \system as learning to solve the kinds of problems that humans
can solve relatively quickly -- once they acquire the relevant domain expertise.
These correspond to short programs -- once you have the right DSL.
Even with the right DSL, program search may be intractable, so
we amortize the cost of program search by training a neural network to
assist the search procedure.

We apply \system to three domains:
 symbolic regression; FlashFill-style~\cite{gulwani2011automating} string processing; and Lisp-style functions on lists.
 For each of these we initially provide a generic
 set of programming primitives in a Lisp-like language.
% including conditionals, variables, and higher-order functions.
 Our algorithm then discovers
 its own domain-specific vocabulary for expressing solutions in the domain (Tbl.~\ref{initialExampleDSL}).
\begin{wrapfigure}{r}{0.6\textwidth}
    \begin{tabular}{ll}
   \toprule
   Domain&Part of the learned DSL\\\midrule
   %% Circuits&\code{(nand (nand a a) (nand b b))}\\
   %% &\hspace{0.5cm} \emph{(an OR gate)}\\
   Regression& \code{(+ (* real x) real)} \\
      &\hspace{0.5cm} \emph{(a linear function of x)}\\
   Strings& \code{(map (lambda (x) (if (= x a) b x)))}\\
   &\hspace{0.5cm} \emph{(replace occurrences of a w/ b)}\\
   Lists& \code{(fold nil (lambda (a b) (cons a b)))}\\
   &\hspace{0.5cm} \emph{(reverses a list)}
   \\\bottomrule
    \end{tabular}
    \caption{ Examples of structure found in DSLs  learned by our algorithm. \system builds a new DSL by discovering and reusing useful subroutines.}\label{initialExampleDSL}\vspace{-1cm}
 \end{wrapfigure}

@@

\begin{wrapfigure}{r}{0.5\textwidth}\vspace{-0.5}
  \begin{tikzpicture}
    \begin{scope}[shift = {(1,-1)}]
    \node[align = center](synthesis) at (6,4) {Search for \\programs};
    \node[align = center](DSL) at (3,1) {DSL};
    \node[align = center](recognitionModel) at (9,1) {Recognition \\model};

>>>>

\begin{figure*}[h]
  \centering
  \begin{tabular}{rc}\toprule
    \sc{Task}& \begin{tabular}{rcl}
      Nancy FreeHafer&$\longrightarrow$&Dr. Nancy\\
      Andrew Cencici&$\longrightarrow$&Dr. Andrew\\
      Pushmeet Kohli&$\longrightarrow$&???
    \end{tabular}
      \\\midrule
    \sc{Program}& $f(\text{\code{s}})\,=\,$\code{(}$f_0$\code{ "Dr." (}$f_2$\code{ s " "))}
      \\\midrule
    \sc{DSL}& \begin{tabular}{l}
      $f_0($\code{a}$,$\code{b}$) \,=\, $\code{(fold a b (lambda (x y) (cons x y)))}\\
      \hspace{0.5cm}($f_0$: \emph{Appends lists (of characters))}\\
      $f_1($\code{s}$,$\code{c}$) \,=\, $\code{(fold s s (lambda (x a)}\\
      \phantom{$f_1($\code{s}$,$\code{c}$) \,=\, $\code{  }}\code{(if (= c x) nil (cons x a))))}\\
      \hspace{0.5cm}($f_1$: \emph{Take characters from }\code{s}\emph{ until }\code{c}\emph{ reached)}
    \end{tabular}
      \\\bottomrule
  \end{tabular}\right.
\end{figure*}

@@

Because any model may be encoded as a (deterministic or probabilistic) program,
we carefully delineate the scope of program learning problems considered here.
We think of \system as learning to solve the kinds of problems that humans
can solve relatively quickly -- once they acquire the relevant domain expertise.
These correspond to short programs if you have an expressive DSL.
Even with such an expressive DSL, program search may be intractable, so
we amortize the cost of program search by training a neural network to
assist the search procedure.

We apply \system to three domains:
 symbolic regression; FlashFill-style~\cite{gulwani2011automating} string processing; and Lisp-style functions on lists.
 For each of these we initially provide a generic
 set of programming primitives in a Lisp-like language.
% including conditionals, variables, and higher-order functions.
 Our algorithm then discovers
 its own domain-specific vocabulary for expressing solutions in the domain (Tbl.~\ref{initialExampleDSL}).
\begin{wrapfigure}{r}{0.6\textwidth}
    \begin{tabular}{ll}
   \toprule
   Domain&Part of the learned DSL\\\midrule
   %% Circuits&\code{(nand (nand a a) (nand b b))}\\
   %% &\hspace{0.5cm} \emph{(an OR gate)}\\
   Regression& \code{(+ (* real x) real)} \\
      &\hspace{0.5cm} \emph{(a linear function of x)}\\
   Strings& \code{(map (lambda (x) (if (= x a) b x)))}\\
   &\hspace{0.5cm} \emph{(replace occurrences of a w/ b)}\\
   Lists& \code{(fold nil (lambda (a b) (cons a b)))}\\
   &\hspace{0.5cm} \emph{(reverses a list)}
   \\\bottomrule
    \end{tabular}
    \caption{ Examples of structure found in DSLs  learned by our algorithm. \system builds a new DSL by discovering and reusing useful subroutines.}\label{initialExampleDSL}
    \vspace{-4em}
 \end{wrapfigure}

@@

\begin{wrapfigure}{r}{0.5\textwidth}
  \begin{tikzpicture}
    \begin{scope}[shift = {(1,-1)}]
    \node[align = center](synthesis) at (6,4) {Search for \\programs};
    \node[align = center](DSL) at (3,1) {DSL};
    \node[align = center](recognitionModel) at (9,1) {Recognition \\model};
